---
title: "Secondtry_Quiz1"
output: html_document
date: '2023-02-28'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("lubridate")
library(tidyverse)
library(Hmisc)
library(patchwork)
library(maps)
library(lubridate)
library(ggplot2)
library(ggmap)

data = read_csv("carbonate_chem_Kaneohe.csv")
View(data)
```

## Is the data tidy.

The data seems fine to me. There are no NAs or zero values. Labels seem clear.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

Date= select(data,c(date,temp))

oct_temp= filter(Date,date == "31-Oct-15")

june_temp= filter(Date,date == "29-Jun-16")

nov_temp= filter(Date,date == "12-Nov-16")

feb_temp= filter(Date,date == "26-Feb-17")

#Calculate each mean and SD indvidually

#October
meanoct_temp=mean(oct_temp$temp)
SDoct_temp=sd(oct_temp$temp)

#June
meanjune_temp=mean(june_temp$temp)
SDjune_temp=sd(june_temp$temp)

#February
meanfeb_temp=mean(feb_temp$temp)
SDfeb_temp=sd(feb_temp$temp)

#November
meannov_temp=mean(nov_temp$temp)
SDnov_temp=sd(feb_temp$temp)

## If there's time
#df1= 


```

## Which survey date had the highest mean seawater temperature? Report mean ± standard deviation seawater temperature for each survey date to support your answer.

October had the highest seawater temperature, as calculated above.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

tadic_data = data %>%
  filter(reefstatus== "Recovery") %>%
  select(reefstatus,ta,dic)
  
View(tadic_data)

tadic_plot =
  ggplot()+
  geom_line(data=tadic_data,aes(x=ta,y=dic))+
  xlab("Total Alkalinity (µmol/kg)")+
  ylab("Dissolved Inorganic Carbon (µmol/kg)")+
  ggtitle("Total Alkalinity vs Dissolved Inorganic Carbon in Kaneohe Bay")+
  scale_x_continuous(limits=c(2100,2200),breaks=seq(2100,2200,20))+
  scale_y_continuous(limits=c(1800,2000),breaks=seq(1800,2000,20))+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(color="black"),
        text = element_text(size=19),
        legend.key = element_blank())

view(tadic_plot)

```

##3) Create a "publishable" plot of TA vs DIC for the "bleached" survey data.
